### 2024-09-25 manuscript.tex
Multiple additions

@@

We analysed a total of about 2421 days of lidar and radiosonde data from 31
voyages and campaigns and one subantarctic station data, covering the Atlantic,
Australian and New Zealand sectors of the SO over the span of 10 years. This
dataset, together with the use of the ALCF lidar simulator, provided a fairly
comprehensive basis for evaluating SO cloud and thermodynamic profile biases in
the GSRM ICON and the ERA5 and MERRA-2 reanalyses. This provides a unique
evaluation perspective different from satellite observations, one which is
more suitable for evaluating bounary layer clouds, which are predominant in
this region. Furthermore, we subsetted our dataset by low and high latitude
bands, cyclonic activity and stability, in order to identify how these
conditions relate the the biases. Our main finding corroborates previous
findings of large boundary layer cloud biases in models, and their subsequent
effect on the radiative transfer. This also applies to the new ICON GSRM,
but the biases are lower than in the reanalyses, despite the reanalyses having
the advantage of assimilation of the observed meteorological conditions.

@@

The RV \emph{Polarstern} data are openly available from Pangaea
(\url{https://pangaea.de}). The MARCUS and Macquarie Island (MICRE) data are
openly available from the Atmospheric Radiation Measurement (ARM)
(\url{https://www.arm.gov}). The MERRA-2 data are openly available from the
NASA NASA Goddard Earth Sciences (GES) Data and Information Services Center
(DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5
data are openly available from the Copernicus Climate Data Store (CDS)
(\url{https://cds.climate.copernicus.eu}). The CERES products are available
from the project website (\url{https://ceres.larc.nasa.gov}) and the NASA
Atmospheric Science Data Centre
(\url{https://asdc.larc.nasa.gov/project/CERES}).  The other voyage and station
data are openly available on Zenodo (). Subsetted model and reanalysis data for
the voyage tracks and the station and data processed with the ALCF are openly
available on Zenodo ().

>>>>

\section{Limitations}

Limitations of our study are numerous. The spatial coverage of our dataset
does not include most parts of the the Indian Ocean and Pacific Ocean sectors
of the SO. Even though climatological features of the SO are typically
relatively uniform zonally, variantions exist, such as those related to the
Antarctic Peninsula and the southern of South America. The voyages were
mostly undertaken in the Austral summer months, and only rarely in the winter
months, due to the poor accesibility of this region during winter. Therefore,
our results are mostly representative of summer, and to lesser extent spring
and autumn conditions.

The time period of ICON is relatively short with only four full years of
simulation available. Moreover, the simulation was free running, which means
that observations had to be temporally mapped to this time period (at the same
time relative to the start of the year) for the comparison. For these reasons,
one can expect the results to be slightly different due to reasons unrelated to
model biases, such as different weather conditions and the phase of climatic
oscillations such as the ENSO in the observations and the model.

Ground-based lidar observations are affected by attenuation by thick cloud
layers, and for this reason the results are mostly representative of BL clouds,
while higher-level clouds are only occassionaly visible to the lidar when BL
are not present. Ground-based lidar observations can be regarded as superior to
satellite lidar observations for low-level clouds in this region, while mid-
and high-level clouds are better represented in satellite observations
\citep{mcerlich2021}.

We attempted to remove lidar profiles with precipitation, which could not be
properly simulated with the lidar simulator (Section \ref{sec:ann}). However,
the approach was limited by relatively low sensitivity of the ANN (65\%), and
the fact that we had to choose a fixed threshold for surface precipitation flux
in the model and renalyses, which might not exactly correspond to detection by
the ANN applied to obseravations. Also, we did not make an attempt to remove
profiles with precipitation not reaching the surface. The above reasons can
result in artificial bias in the comparison, even though we exect this to be
much smaller than the identified model biases.

@@

We analysed a total of about 2421 days of lidar and radiosonde data from 31
voyages and campaigns and one subantarctic station data, covering the Atlantic,
Australian and New Zealand sectors of the SO over the span of 10 years. This
dataset, together with the use of the ALCF lidar simulator, provided a fairly
comprehensive basis for evaluating SO cloud and thermodynamic profile biases in
the GSRM ICON and the ERA5 and MERRA-2 reanalyses. This provides a unique
evaluation perspective different from satellite observations, one which is
more suitable for evaluating bounary layer clouds, which are predominant in
this region. Furthermore, we subsetted our dataset by low and high latitude
bands, cyclonic activity and stability, in order to identify how these
conditions relate the the biases. Our main finding corroborates previous
findings of large boundary layer cloud biases in models, and their subsequent
effect on the radiative transfer. This also applies to the new ICON GSRM,
but the biases are lower than in the reanalyses, despite the reanalyses having
the advantage of assimilation of the observed meteorological conditions.
The GSRM has, on the other hand, the advange of a much higher spatial
resolution and, to some extent, explicit calculation of traditionally
subgrid-scale processes such as convection.

The relationship between cloud biases and radiation has a number of notable
features. Perhaps unsurprisingly, The reanalyses exhibit the too few,
too bright type of bias previously identified in models. In our results,
this is characterised by outgoing SW radiation similar to or higher
than in satellite observations, while at the same time total cloud fraction
is substantially underestimated relative to the ground-based lidar observation.
This feature seems to be much more pronounced in ERA5 than in MERRA-2. On
the other hand, this type of relationship is not present in ICON. This model
mostly predicts smaller outgoing SW radiation and smaller total cloud fraction
than observations, and the deficit of outgoing SW radiation is approximately
proportial to the deficit of the total cloud fraction. While this might be a
welcome feature and an improvement over previous models, it does mean that the
outgoing SW radiation is overall underestimated, instead of being compensated
by a higher cloud albedo. This can, of course, lead to undesirable secondary
effects such as overestimated solar heating of the sea surface, but a
combination of many factors have been found to be responsible for SO SST biases
in climate models \citep{zhang2023,luo2023}.

@@

The RV \emph{Polarstern} data are openly available from Pangaea
(\url{https://pangaea.de}). The MARCUS and Macquarie Island (MICRE) data are
openly available from the Atmospheric Radiation Measurement (ARM)
(\url{https://www.arm.gov}). The MERRA-2 data are openly available from the
NASA Goddard Earth Sciences (GES) Data and Information Services Center
(DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5
data are openly available from the Copernicus Climate Data Store (CDS)
(\url{https://cds.climate.copernicus.eu}). The ICON data are available on the
Levante cluster of the Deutsches Klimarechenzentrum (DKRZ;
\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at
\url{https://luv.dkrz.de/register/}. The CERES products are available from the
project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric
Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}). The other
voyage and station data are openly available on Zenodo (). Subsetted model and
reanalysis data for the voyage tracks and the station and data processed with
the ALCF are openly available on Zenodo ().
